Complex Quasiperiodic Pre-Main-Sequence M-Dwarfs from Four Years of TESS

### 2023-06-13 paper/ms.tex
update ms

\title{Complex Quasiperiodic Variables from Four Years of TESS}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence
  M-dwarfs with almost-periodic optical modulation that includes both
  sharp and broad troughs.  The troughs are usually superposed over
  smooth, spot-like modulation.  Based on a lack of observed infrared
  excesses, these objects do not have primordial gas-rich disks.
  Nonetheless, the currently preferred explanations for their optical
  variability invoke long-lived material in orbit at the corotation
  radius, for instance transiting dust clumps or stellar prominences.
  Here, we report new CQVs discovered in TESS data collected between
  July~2018 and Sep~2022.  Our search used two methods, the first
  based on counting dips in phase-folded light curves, and the second
  based on counting peaks in the Fourier domain.  From our analysis of
  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
  and they include the brightest ($T$$\approx$10) and closest
  ($d$$\approx$20\,pc) examples of this class of object known.  A few
  objects are ``outliers among outliers''; for instance LP 12-502
  shows four to eight local minima per cycle, distributed over a ``dip
  complex'' with a total duration that is fixed over more than one
  thousand cycles, but with a detailed shape that exhibited changes
  over less than one cycle.  More generally, we find that none of the
  CQVs maintain a fixed light curve shape over timescales of more than
  a few hundred cycles -- hence, {\it quasi}periodic.  Although the
  physical explanation behind these objects remains enigmatic, our
  sample may help clarify their origin.  Connections to star, disk,
  and exoplanet evolution are emphasized.
\end{abstract}

>>>>

\title{Complex Quasiperiodic Pre-Main-Sequence M-Dwarfs from Four Years of TESS}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence
  M-dwarfs with almost-periodic optical modulation that includes both
  sharp and broad troughs.  The troughs are usually superposed over
  smooth, spot-like modulation.  These objects do not have primordial
  gas-rich disks, based on a lack of observed infrared excesses.
  Nonetheless, the currently preferred explanations for their optical
  variability invoke long-lived material in orbit at the corotation
  radius, for instance transiting dust clumps or stellar prominences.
  Here, we report new CQVs discovered in TESS data collected between
  July~2018 and Sep~2022.  Our search used two methods, the first
  based on counting dips in phase-folded light curves, and the second
  based on counting peaks in the Fourier domain.  From our analysis of
  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
  and they include the brightest ($T$$\approx$10) and closest
  ($d$$\approx$20\,pc) examples of this class of object known.  A few
  objects are ``outliers among outliers''; for instance LP 12-502
  shows four to eight local minima per cycle, distributed over a ``dip
  complex'' with a total duration that is fixed over more than one
  thousand cycles, but with a detailed shape that exhibited changes
  over less than one cycle.  More generally, we find that none of the
  CQVs maintain a fixed light curve shape over timescales of more than
  a few hundred cycles -- hence, {\it quasi}periodic.  Although the
  physical explanation behind these objects remains enigmatic, our
  sample may help clarify their origin.  Connections to star, disk,
  and exoplanet evolution are emphasized.
\end{abstract}
